Bayesian Inference Using Sequential Monte-Carlo Algorithm for Dynamic System Models

### 2020-08-01 MSc-dissertation.tex
Fix fig

    \caption{Estimated posterior distribution of parameters in model 3}
    \label{fig:para1}

@@

        \caption{Model comparison of model 1, 2 and 3}
        \label{fig:cmp1}

@@

\begin{table}[t!]
    \centering
    \begin{tabular}{|c c c|} 
     \hline
     Parameter & Estimated mean  & Estimated mean  \\ 
      & value (uniform) &value (log-uniform) \\[0.5ex] 
     \hline\hline
     $\lambda_N$ & 14.156 & 13.296  \\ 
     $a$ & 9.670 & 0.017  \\ 
     $\kappa_{N\beta}$ & 18.001 & 0.259 \\
     $\mu_N$ & 13.196 & 0.018 \\
     $\nu_{N\Phi}$ & 0.742 & 0.131 \\
     \hline
     $\kappa_{\Phi\beta}$ & 0.239 & 0.156 \\
     $\mu_\Phi$ & 0.154 & 0.035 \\
     \hline
     $s_{\beta N}$ & 6.752 & 1.213 \\
     $\mu_\beta$ & 6.378 & 1.315 \\
     \hline
     $s_{\alpha\Phi}$ & 16.997 & 5.826 \\
     $\mu_\alpha$ & 11.859 & 2.434\\
     \hline
    \end{tabular}
    \caption{Estimated parameter values of model 3}
    \label{table:estimated1}
\end{table}

@@

\begin{table}[h!]
    \centering
    \begin{tabular}{|c c c|} 
     \hline
     Parameter & Value & Unit\\ [0.5ex] 
     \hline\hline
     $\lambda_N$ & 2.1989 & $cell/h$  \\ 
     $\kappa_{N\beta}$ & 3.9627 & $cell/(unit\cdotp h)$\\
     $\mu_N$ & 1.7219 & $h^{-1}$\\
     $\nu_{N\Phi}$ & 0.2195 & $cell^{-1}\cdotp h^{-1}$ \\
     \hline
     $\lambda_\Phi$ & 1.3146 & $cell/h$ \\
     $\kappa_{\Phi\beta}$ & 0.1235 & $cell/(unit\cdotp h)$ \\
     $\mu_\Phi$ & 0.1454 & $h^{-1}$ \\
     \hline
     $s_{\beta N}$ & 6.5536 & $unit/(cell\cdotp h)$ \\
     $i_{\beta\Phi}$ & 1.7062 & $cell^{-1}$ \\
     $\mu_\beta$ & 0.5212 & $h^{-1}$ \\
     \hline
     $s_{\alpha\Phi}$ & 10.2416 & $unit/(cell\cdotp h)$ \\
     $\mu_\alpha$ & 19.6642 & $h^{-1}$ \\
    [1ex] 
     \hline
    \end{tabular}
    \caption{Parameter values used for model 1}
    \label{table:m1}
\end{table}

>>>>

    \caption[Estimated posterior distribution of parameters in model 3]%
    {Estimated posterior distribution of parameters in model 3. Shaded range indicates 25\%--75\% quantile of the population}
    \label{fig:para1}

@@

        \caption[Model comparison of model 1, 2 and 3]%
        {Model comparison of model 1, 2 and 3. From population 8 to population 30, model3 always wins}
        \label{fig:cmp1}

@@

\begin{table}[t!]
    \centering
    \begin{tabular}{|c c c|} 
     \hline
     Parameter & Estimated mean  & Estimated mean  \\ 
      & value (uniform) &value (log-uniform) \\[0.5ex] 
     \hline\hline
     $\lambda_N$ & 14.1 & 13.3 \\ 
     $a$ & 9.67 & 0.0170  \\ 
     $\kappa_{N\beta}$ & 18.0 & 0.259 \\
     $\mu_N$ & 13.2 & 0.0180 \\
     $\nu_{N\Phi}$ & 0.742 & 0.131 \\
     \hline
     $\kappa_{\Phi\beta}$ & 0.239 & 0.156 \\
     $\mu_\Phi$ & 0.154 & 0.0350 \\
     \hline
     $s_{\beta N}$ & 6.75 & 1.21 \\
     $\mu_\beta$ & 6.38 & 1.32 \\
     \hline
     $s_{\alpha\Phi}$ & 17.0 & 5.83 \\
     $\mu_\alpha$ & 11.9 & 2.43\\
     \hline
    \end{tabular}
    \caption[Estimated parameter values of model 3]
    {Estimated parameter values of model 3, using uniform prior distribution and log-uniform prior distribution respectively}
    \label{table:estimated1}
\end{table}

@@

\begin{table}[h!]
    \centering
    \begin{tabular}{|c c c|} 
     \hline
     Parameter & Value & Unit\\ [0.5ex] 
     \hline\hline
     $\lambda_N$ & 2.20 & $cell/h$  \\ 
     $\kappa_{N\beta}$ & 3.9627 & $cell/(unit\cdotp h)$\\
     $\mu_N$ & 1.7219 & $h^{-1}$\\
     $\nu_{N\Phi}$ & 0.2195 & $cell^{-1}\cdotp h^{-1}$ \\
     \hline
     $\lambda_\Phi$ & 1.3146 & $cell/h$ \\
     $\kappa_{\Phi\beta}$ & 0.1235 & $cell/(unit\cdotp h)$ \\
     $\mu_\Phi$ & 0.1454 & $h^{-1}$ \\
     \hline
     $s_{\beta N}$ & 6.5536 & $unit/(cell\cdotp h)$ \\
     $i_{\beta\Phi}$ & 1.7062 & $cell^{-1}$ \\
     $\mu_\beta$ & 0.5212 & $h^{-1}$ \\
     \hline
     $s_{\alpha\Phi}$ & 10.2416 & $unit/(cell\cdotp h)$ \\
     $\mu_\alpha$ & 19.6642 & $h^{-1}$ \\
    [1ex] 
     \hline
    \end{tabular}
    \caption{Parameter values used for model 1}
    \label{table:m1}
\end{table}
